Inpainting with controlled dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Removed assertion again

\section{Results}
We evaluated two versions of our algorithm: An iterative variant and a non-iterative variant.
Our iterative variant repeats 
 ((( TODO )))

 We compare our algorithm with the following two baseline algorithms:
 \begin{enumerate}
	 \item A simple linear inpainting algorithm using the nearest neighbor pixels.
	 \item A matching pursuit algorithm \cite{matchingpursuit93} with an overcomplete dictionary consisting of Discrete Cosine transforms.
 \end{enumerate}

@@

When reporting computational or measurement results, always
report the mean (average value) along with a measure of variablility
(standard deviation(s) or standard error of the mean).

>>>>

\section{Results}

 ((( TODO )))

 We compare our algorithm with the following two baseline algorithms:
 \begin{enumerate}
	 \item A simple linear inpainting algorithm using the nearest neighbor pixels.
	 \item A matching pursuit algorithm \cite{matchingpursuit93} with an overcomplete dictionary built with Discrete Cosine transforms.
 \end{enumerate}

  Our algorithm is resistant to high percentages of missing pixels, the average error per missing pixel rises only slowly until ((( TODO level))).

@@

When reporting computational or measurement results, always
report the mean (average value) along with a measure of variablility
(standard deviation(s) or standard error of the mean). ((( TODO !!! )))
